---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
	1. Unzip the compressed file
	2. Load the CSV file
	3. Convert Date column to Date format
	
```{r echo=TRUE}
	unzip("repdata-data-activity.zip")
	Data <- read.csv("C:\\Users\\Kawthar\\Documents\\Data Science\\Reproducible Research\\Week 2\\project\\activity.csv")
	Data$date <- as.Date(Data$date, "%Y-%m-%d")
```


## What is mean total number of steps taken per day?

1. Aggregate the data on interesting variables and calculate the mean
```{r echo=TRUE}
	AGG_DATA <- aggregate(steps ~ date, data=Data, FUN=sum, na.rm=TRUE)
```
2. Plot the histogram
```{r fig.width=15, echo=TRUE}
	hist(AGG_DATA$steps)
```
3. Calculate Mean and Median


```{r echo=TRUE}
	MEAN <- mean(AGG_DATA$steps, na.rm=FALSE)
	MEDIAN <- median(AGG_DATA$steps, na.rm=FALSE)
```

```{r echo=FALSE}
	MEAN <- mean(AGG_DATA$steps, na.rm=FALSE)
	MEDIAN <- median(AGG_DATA$steps, na.rm=FALSE)
```

## What is the average daily activity pattern?

1. Calculate mean value 
```{r echo=FALSE}
	AGG_DATA_MEAN <- aggregate(steps ~ interval, data=Data, FUN=mean, na.rm=TRUE)
	plot(AGG_DATA_MEAN$interval, AGG_DATA_MEAN$steps, type="l")


	MEAN_MAX <- which.max(AGG_DATA_MEAN$steps)
	AGG_DATA_MEAN$interval[MEAN_MAX]
```

## Imputing missing values

```{r echo=FALSE}

	COUNT_NA <- sum(is.na(Data$steps))
	COUNT_NA
	
	Data_2 <- Data
	Data_2$steps[is.na(Data_2$steps)] <- 0
	hist(Data_2$steps)
```

```{r echo=TRUE}

	COUNT_NA <- sum(is.na(Data$steps))
	COUNT_NA
	
	strategy (not clear)!
	Data_2 <- Data
	Data_2$steps[is.na(Data_2$steps)] <- 0
	hist(Data_2$steps)
```
## Are there differences in activity patterns between weekdays and weekends?

```{r echo=FALSE}

	Data$DayType <- as.factor(ifelse(weekdays(Data$date) %in% c("Saturday","Sunday"),"weekend", "weekday"))
	WEEKDAY_DATA <- Data[Data$DayType=="weekday" , ]
	AGG_DATA_WEEKDAY <- aggregate(steps ~ interval, data=WEEKDAY_DATA, FUN=sum, na.rm=TRUE)
	
	WEEKENDDAY_DATA <- Data[Data$DayType=="weekend" , ]
	AGG_DATA_WEEKENDDAY <- aggregate(steps ~ interval, data=WEEKENDDAY_DATA, FUN=sum, na.rm=TRUE)
```

```{r echo=TRUE}

	par(mfrow=c(1,2))
	plot(AGG_DATA_WEEKDAY$interval, AGG_DATA_WEEKDAY$steps, type="l")
	plot(AGG_DATA_WEEKENDDAY$interval, AGG_DATA_WEEKENDDAY$steps, type="l")
```